---
title: "matplotlib demo"
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE)
```

```{r}
library(reticulate)
```

For a demonstration of a line plot on a polar axis, see @fig-polar.

```{python}
#| label: fig-polar
#| fig-cap: "A line plot on a polar axis"
#| message: false

import numpy as np
import matplotlib.pyplot as plt

r = np.arange(0, 2, 0.01)
theta = 2 * np.pi * r
fig, ax = plt.subplots(
  subplot_kw = {'projection': 'polar'} 
)
ax.plot(theta, r)
ax.set_rticks([0.5, 1, 1.5, 2])
ax.grid(True)
plt.show()
```

No están usando objetos compartidos en este ejemplo, pero también se podrían hacer como en el ejemplo con R Markdown.

**Quarto** es muy parecido a R Markdown: [Página oficial de Quarto](https://quarto.org)

## Air Quality

@fig-airquality further explores the impact of temperature on ozone level.

```{r}
#| label: fig-airquality
#| fig-cap: Temperature and ozone level.
#| warning: false
#| fig-width: 8
#| fig-height: 4

library(ggplot2)

ggplot(airquality, aes(Temp, Ozone)) + 
  geom_point() + 
  geom_smooth(method = "loess"
)
```

## Incluye otros lenguajes: observable

**Seattle Precipitation by Day (2012 to 2016)**

```{r}
#| eval: false
# https://github.com/vega/vega/blob/main/docs/data/seattle-weather.csv
download.file(
  url="https://raw.githubusercontent.com/vega/vega/main/docs/data/seattle-weather.csv",
  destfile = "seattle-weather.csv")
```


```{ojs}
data = FileAttachment("seattle-weather.csv")
  .csv({typed: true})
  
Plot.plot({
  width: 800, height: 500, padding: 0,
  color: { scheme: "blues", type: "sqrt"},
  y: { tickFormat: i => "JFMAMJJASOND"[i] },
  marks: [
    Plot.cell(data, Plot.group({fill: "mean"}, {
      x: d => d.date.getUTCDate(),
      y: d => d.date.getUTCMonth(),
      fill: "precipitation", 
      inset: 0.5
    }))
  ]
})
```
